A multi-scale story of the diffusion of a new technology: the web

### 2024-06-11 presentations/web_diffusion.Rmd
path

<!-- ![](C:/Users/nw19521/OneDrive%20-%20University%20of%20Bristol/projects/archive/nuts/figure/Picture1.png){width="70%"} -->

![](/Users/nw19521/Library/CloudStorage/OneDrive-UniversityofBristol/projects/archive/nuts/figure/Picture1.png){width="70%"}

@@

<!-- ![](C:/Users/nw19521/OneDrive%20-%20University%20of%20Bristol/projects/archive/nuts/figure/Picture2.png){width="70%"} -->

![](/Users/nw19521/Library/CloudStorage/OneDrive-UniversityofBristol/projects/archive/nuts/figure/Picture2.png){width="70%"}

>>>>

<!-- ![](C:/Users/nw19521/OneDrive%20-%20University%20of%20Bristol/projects/archive/nuts/figure/Picture1.png){width="70%"} -->
<!-- ![](/Users/nw19521/Library/CloudStorage/OneDrive-UniversityofBristol/projects/archive/nuts/figure/Picture1.png){width="70%"} -->
![](images/Picture1.png){width="70%"}

@@

<!-- ![](C:/Users/nw19521/OneDrive%20-%20University%20of%20Bristol/projects/archive/nuts/figure/Picture2.png){width="70%"} -->
<!-- ![](/Users/nw19521/Library/CloudStorage/OneDrive-UniversityofBristol/projects/archive/nuts/figure/Picture2.png){width="70%"} -->
![](images/Picture2.png){width="70%"}
